---
title: "Take-home Exercise 6"
description: |
  Network Analysis
author:
  - name: LI HONGYI 
    url: 
    affiliation: SMU SCIS
    affiliation_url: https://scis.smu.edu.sg
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

In this take-home exercise, the main task is to visualize the social network of Ohio, USA.

## install packages

```{r}
packages = c('igraph','tidygraph','ggraph','visNetwork',
             'lubridate','clock','tidyverse','graphlayouts')
for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```

## import data

```{r eval=FALSE, include=FALSE}
participants <- read_csv("data/Participants.csv")
edges <- read_csv("data/SocialNetwork.csv")
```

## wrangling attribute

```{r eval=FALSE, include=FALSE}
participants <- 
  read_rds("data/rds/participants.rds")

edge_aggregated <- edges %>%
  group_by(participantIdFrom, participantIdTo) %>%
  summarise(Weight = n()) %>%
  filter(participantIdFrom != participantIdTo) %>%
  filter(Weight > 200) %>%
  ungroup
```

```{r eval=FALSE, include=FALSE}
nodes <- edge_aggregated %>% 
  select(participantIdFrom) %>%
  group_by(participantIdFrom) %>%
  summarise(Weight = n()) %>%
  select(participantIdFrom) %>% 
  rename(participantId = participantIdFrom)

nodes_aggregated <- merge(x = nodes, y = participants, by = "participantId")
```

```{r eval=FALSE, include=FALSE}
write_rds(edge_aggregated,
          "data/rds/edge_aggregated.rds")
write_rds(nodes_aggregated,
          "data/rds/nodes_aggregated.rds")
```

```{r}
edge_aggregated <- 
  read_rds("data/rds/edge_aggregated.rds")
nodes_aggregated <- 
  read_rds("data/rds/nodes_aggregated.rds")
```

## Buildling graph model

```{r}
cgraph <- graph_from_data_frame(edge_aggregated,
                                vertices = nodes_aggregated) %>%
  as_tbl_graph
cgraph
```
## Ploting the graph
### social network (weight>200, color = interest group)
```{r,  fig.width=10, fig.height=10}
ggraph(cgraph,
       layout = "stress") +
  geom_edge_link(aes(width = Weight),
                 alpha = 0.1) +
  scale_edge_width(range = c(0.5, 1.5)) + 
  geom_node_point(
    aes(colour=interestGroup, size = 1)) +
  theme_graph()

```

```{r,  fig.width=10, fig.height=10}
ggraph(cgraph,
       layout = "nicely") +
  geom_edge_link(aes(width = Weight),
                 alpha = 0.1) +
  scale_edge_width(range = c(0.5, 1.5)) + 
  geom_node_point(
    aes(colour=interestGroup, size = 1)) +
  theme_graph()

```
### social network (weight >200, color = education level)

```{r,  fig.width=10, fig.height=10}
ggraph(cgraph,
       layout = "nicely") +
  geom_edge_link(aes(width = Weight),
                 alpha = 0.1) +
  scale_edge_width(range = c(0.5, 1.5)) + 
  geom_node_point(
    aes(colour=educationLevel, size = 1)) +
  theme_graph()

```

```{r,  fig.width=10, fig.height=10}
set_graph_style()

g<- ggraph(cgraph,
           layout = "nicely") + 
  geom_edge_link(aes(width = Weight),
                 alpha = 0.2) +
  scale_edge_width(range = c(0.5, 2)) + 
  geom_node_point(
    aes(colour=interestGroup), size = 2) 
 
g + facet_nodes(~educationLevel)+ 
    th_foreground(foreground = "grey80",
                  border = TRUE)+
  theme(legend.position = "bottom")
```

```{r,  fig.width=10, fig.height=10}
set_graph_style()

g<- ggraph(cgraph,
           layout = "nicely") + 
  geom_edge_link(aes(width = Weight),
                 alpha = 0.2) +
  scale_edge_width(range = c(0.5, 2)) + 
  geom_node_point(
    aes(colour=educationLevel), size = 2) 
 
g + facet_nodes(~interestGroup)+ 
    th_foreground(foreground = "grey80",
                  border = TRUE)+
  theme(legend.position = "bottom")
```

## Social Network with more frequent interactivity (>300)
```{r}
participants <- 
  read_rds("data/rds/participants.rds")
```

```{r}
edge_aggregated_less <- edge_aggregated %>%
  filter(Weight > 300)

nodes_less <- edge_aggregated_less %>% 
  select(participantIdFrom) %>%
  group_by(participantIdFrom) %>%
  summarise(Weight = n()) %>%
  select(participantIdFrom) %>% 
  rename(participantId = participantIdFrom)

nodes_aggregated_less <- merge(x = nodes_less, y = participants, by = "participantId")
```

```{r}
cgraph_less <- graph_from_data_frame(edge_aggregated_less,
                                vertices = nodes_aggregated_less) %>%
  as_tbl_graph
cgraph_less
```


```{r,  fig.width=10, fig.height=10}
ggraph(cgraph_less,
       layout = "stress") +
  geom_edge_link(aes(width = Weight),
                 alpha = 0.1) +
  scale_edge_width(range = c(0.5, 1.5)) + 
  geom_node_point(
    aes(colour=interestGroup, size = 1)) +
  theme_graph()

```

```{r,  fig.width=10, fig.height=10}
ggraph(cgraph_less,
       layout = "nicely") +
  geom_edge_link(aes(width = Weight),
                 alpha = 0.1) +
  scale_edge_width(range = c(0.5, 1.5)) + 
  geom_node_point(
    aes(colour=educationLevel, size = 1)) +
  theme_graph()

```

```{r,  fig.width=10, fig.height=10}
set_graph_style()

g<- ggraph(cgraph_less,
           layout = "nicely") + 
  geom_edge_link(aes(width = Weight),
                 alpha = 0.2) +
  scale_edge_width(range = c(0.5, 2)) + 
  geom_node_point(
    aes(colour=interestGroup), size = 2) 
 
g + facet_nodes(~educationLevel)+ 
    th_foreground(foreground = "grey80",
                  border = TRUE)+
  theme(legend.position = "bottom")
```

## Social Network with more frequent interactivity (>400)

```{r}
edge_aggregated_least <- edge_aggregated %>%
  filter(Weight > 400)

nodes_least <- edge_aggregated_least %>% 
  select(participantIdFrom) %>%
  group_by(participantIdFrom) %>%
  summarise(Weight = n()) %>%
  select(participantIdFrom) %>% 
  rename(participantId = participantIdFrom)

nodes_aggregated_least <- merge(x = nodes_least, y = participants, by = "participantId")
```

```{r}
cgraph_least <- graph_from_data_frame(edge_aggregated_least,
                                vertices = nodes_aggregated_least) %>%
  as_tbl_graph
cgraph_least
```


```{r,  fig.width=10, fig.height=10}
ggraph(cgraph_least,
       layout = "stress") +
  geom_edge_link(aes(width = Weight),
                 alpha = 0.1) +
  scale_edge_width(range = c(0.5, 1.5)) + 
  geom_node_point(
    aes(colour=interestGroup, size = 1)) +
  theme_graph()

```

```{r,  fig.width=10, fig.height=10}
ggraph(cgraph_least,
       layout = "nicely") +
  geom_edge_link(aes(width = Weight),
                 alpha = 0.1) +
  scale_edge_width(range = c(0.5, 1.5)) + 
  geom_node_point(
    aes(colour=interestGroup, size = 1)) +
  theme_graph()

```